---
title: "Infant language exposure and language networks"
author: "Lucy King"
date: "2/4/2020"
output: html_document
---

# Environment set up 
```{r}
library(tidyverse)
library(corrr)
library(sjstats)
library(psych)
library(ggcorrplot)
library(car)
library(ggsci)
library(BayesFactor)
# for meff function
source('https://osf.io/ws6xc/download')

data_home_personal <- "~/Box/lucy_king_files/BABIES/rsfMRI/data/"
data_home_mooddata <- "~/Box/Mooddata_Coordinating/BABIES/Data/final_scored_data/"

rs_file <- paste0(data_home_personal, "language/coherence_tidy_20200203.csv")
fd_file <- paste0(data_home_personal, "summarized_fd.csv")
demo_file <- paste0(data_home_mooddata, "demographics/demo_6mo_cleaned_final.csv")
lena_file <- paste0(data_home_mooddata, "LENA/lena_final_wf_day1day2_20200208.csv")
scanner_file <- paste0(data_home_personal, "6mo_scanner_20200209.csv")
shipley_file <- paste0(data_home_personal,"language/shipley_6mo_final_20200208.csv")
nutrition_file <- paste0(data_home_personal, "HOME_nutrition_cleaned_20200208.csv")
prams_file <- paste0(data_home_mooddata, "PRAMS/prams_alldata_cleaned.csv")
ibq_file <- paste0(data_home_mooddata, "IBQ/ibq_scored_final.csv")
digit_span_file <- paste0(data_home_personal, "digit_span_6mo_complete.csv")

  
theme_lena <-
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    plot.title = element_text(size = 18, hjust = .5),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 16),
    legend.title = element_text(size = 18), 
    legend.text = element_text(size = 16),
    legend.position = "bottom"
  )

options(scipen = 999)
```

# Read in data

```{r}
d <-
  read_csv(demo_file) %>%  
  left_join(read_csv(lena_file), by = "ID") %>% 
  left_join(read_csv(rs_file), by = "ID") %>% 
  left_join(read_csv(fd_file), by = "ID") %>% 
  left_join(read_csv(scanner_file), by = "ID") %>% 
  left_join(read_csv(shipley_file), by = "ID") %>% 
  left_join(read_csv(nutrition_file), by = "ID") %>% 
  left_join(read_csv(digit_span_file), by = "ID") %>% 
  left_join(read_csv(prams_file), by = "ID") %>%  
  left_join(read_csv(ibq_file), by = "ID") %>% 
  rename(
    age_1_lena = age_1,
    age_2_lena = age_2
  ) %>% 
  mutate(
    pregnancy_weight_diff = if_else(
      !is.na(preg_weight_gain),
      preg_weight_gain, -1 * preg_weight_loss
    ),
    primary_english = if_else(
      primarylang == "English",
      1, 0
    ),
    age_diff_lena_scan_1 = age_scan - age_1_lena,
    age_diff_lena_scan_2 = age_scan - age_2_lena,
    white = if_else(
      mom_race == "White",
      1, 0
    ),
    age_diff_lab_scan = age_scan - age_behav
  )
```

# Participants

### Compare included vs. not on LENA and covariates
```{r}
d <-
  d %>% 
  mutate(
    included = !is.na(front_coherence_z) & !is.na(ctc_hour_max_1)
  )

d %>% 
  count(included)
```

```{r}
# mom characteristics
t.test(d$mom_age ~ d$included)
t.test(d$income_needs ~ d$included)
t.test(d$education ~ d$included)
t.test(d$shipley_6mo_total ~ d$included)
t.test(d$digitspan_totalscore ~ d$included)
t.test(d$prev_preg_total ~ d$included)
t.test(d$pregnancy_weight_diff ~ d$included)
```

```{r}
# baby chracteristics
t.test(d$age_scan ~ d$included)
t.test(d$age_scan_corr ~ d$included)
t.test(d$gestational_weeks_birth ~ d$included)
t.test(d$NEG ~ d$included)
t.test(d$SUR ~ d$included)
t.test(d$REG ~ d$included)
t.test(d$birth_weight_total_lbs ~ d$included)
```

```{r}
# LENA
t.test(d$ctc_hour_max_1 ~ d$included)
t.test(d$awc_hour_max_1 ~ d$included)
t.test(d$cvc_hour_max_1 ~ d$included)
t.test(d$ctc_prop_1 ~ d$included)
t.test(d$awc_prop_1 ~ d$included)
```

```{r}
# categorical variables 
chisq.test(d$included, d$male)
chisq.test(d$included, d$mom_latinx)
chisq.test(d$included, d$baby_latinx)
chisq.test(d$included, d$white)
chisq.test(d$included, d$scanner_6mo)
chisq.test(d$included, d$breastfed)
chisq.test(d$included, d$now_breastfed)
chisq.test(d$included, d$primary_english)
```


```{r}
d_sample <-
  d %>% 
  filter(included == TRUE)

d_sample %>% 
  count(primarylang)

d_sample %>% 
  count(scanner_6mo)

d_sample %>% 
  count(breastfed) %>% 
  mutate(
    per = n / sum(n)
  )
```
## Distance between scan, lab session, and LENA assessment
```{r}
d_sample %>% 
  ggplot(aes(age_diff_lena_scan_1)) +
  geom_histogram()

d_sample %>% 
  ggplot(aes(age_diff_lab_scan)) +
  geom_histogram()

d_sample %>% 
  mutate(
    age_diff_lena_scan_1 = age_diff_lena_scan_1 * 4,
    age_diff_lab_scan = age_diff_lab_scan * 4
  ) %>% 
  summarise_at(
    vars(age_diff_lena_scan_1, age_diff_lab_scan),
    funs(mean, sd), na.rm = TRUE
  )
```

## Table 1
```{r}
d_sample_means <-
  d_sample %>% 
  summarise_at(
    vars(
      age_scan,
      gestational_age,
      birth_weight_total_lbs,
      NEG,
      mom_age,
      prev_preg_total,
      income_needs,
      digitspan_totalscore,
      shipley_6mo_total,
      awc_hour_max_1,
      ctc_hour_max_1,
      awc_prop_1,
      ctc_prop_1,
      cvc_hour_max_1,
      front_coherence_z,
      temp_coherence_z
    ),
    funs(mean), na.rm = TRUE
  ) %>% 
  gather(variable, mean, age_scan:temp_coherence_z)

d_sample_sds <-
  d_sample %>% 
  summarise_at(
    vars(
      age_scan,
      gestational_age,
      birth_weight_total_lbs,
      NEG,
      mom_age,
      prev_preg_total,
      income_needs,
      digitspan_totalscore,
      shipley_6mo_total,
      awc_hour_max_1,
      ctc_hour_max_1,
      awc_prop_1,
      ctc_prop_1,
      cvc_hour_max_1,
      front_coherence_z,
      temp_coherence_z
    ),
    funs(sd), na.rm = TRUE
  ) %>% 
  gather(variable, sd, age_scan:temp_coherence_z)

d_sample_mins <-
  d_sample %>% 
  summarise_at(
    vars(
      age_scan,
      gestational_age,
      birth_weight_total_lbs,
      NEG,
      mom_age,
      prev_preg_total,
      income_needs,
      digitspan_totalscore,
      shipley_6mo_total,
      awc_hour_max_1,
      ctc_hour_max_1,
      awc_prop_1,
      ctc_prop_1,
      cvc_hour_max_1,
      front_coherence_z,
      temp_coherence_z
    ),
    funs(min), na.rm = TRUE
  ) %>% 
  gather(variable, min, age_scan:temp_coherence_z)

d_sample_maxs <-
  d_sample %>% 
  summarise_at(
    vars(
      age_scan,
      gestational_age,
      birth_weight_total_lbs,
      NEG,
      mom_age,
      prev_preg_total,
      income_needs,
      digitspan_totalscore,
      shipley_6mo_total,
      awc_hour_max_1,
      ctc_hour_max_1,
      awc_prop_1,
      ctc_prop_1,
      cvc_hour_max_1,
      front_coherence_z,
      temp_coherence_z
    ),
    funs(max), na.rm = TRUE
  ) %>% 
  gather(variable, max, age_scan:temp_coherence_z)

d_sample_means %>% 
  left_join(d_sample_sds, by = "variable") %>% 
  left_join(d_sample_mins, by = "variable") %>% 
  left_join(d_sample_maxs, by = "variable")
```

```{r}
d_sample %>% 
  count(male)

d_sample %>% 
  count(primary_english)

d_sample %>% 
  count(education_txt)

d_sample %>% 
  count(mom_race)

d_sample %>% 
  count(mom_latinx)
```

# Corrected p-value
```{r}
lena_d <-
  d_sample %>% 
  select(
    ctc_prop_1,
    awc_prop_1,
    ctc_hour_max_1,
    awc_hour_max_1
  )

meff_lena <- meff(lena_d)

.05/meff_lena
```

# Correlations and t-tests

## LENA measures
```{r}
lena_corr <- 
  d_sample %>% 
  select(
    ctc_prop_1,
    awc_prop_1,
    ctc_hour_max_1,
    awc_hour_max_1,
    cvc_hour_max_1,
    age_1_lena,
    age_scan_corr,
    gestational_weeks_birth,
    birth_weight_total_lbs,
    education,
    mom_age,
    income_needs,
    shipley_6mo_total,
    digitspan_totalscore,
    pregnancy_weight_diff,
    NEG,
    age_diff_lena_scan_1
  ) %>% 
  correlate(method = "spearman") %>% 
  mutate_at(
    vars(-rowname),
    funs(round(., 3))
  )

write_csv(lena_corr, paste0(data_home_personal, "language/lena_covariates.csv"))
```

```{r}
lena_corr_plot <- 
  d_sample %>% 
  select(
    `Infant vocalizations` = cvc_hour_max_1,
    `CT consistency` = ctc_prop_1,
    `AW consistency` = awc_prop_1,
    `CT quantity` = ctc_hour_max_1,
    `AW quantity` = awc_hour_max_1
  ) %>% 
  cor(method = "pearson") 

ggcorrplot(
  lena_corr_plot,
  hc.order = FALSE, 
  digits = 2, 
  lab = TRUE, 
  type = "upper",
  legend.title = "Pearson\ncorrelation coefficient",
  tl.cex = 16,
  lab_size = 6
  )

ggsave(paste0(data_home_personal, "language/lena_corr_plot.png"))
```

```{r}
# intercorrelations
cor.test(d_sample$awc_hour_max_1, d_sample$awc_prop_1)
cor.test(d_sample$ctc_hour_max_1, d_sample$awc_prop_1)

cor.test(d_sample$awc_hour_max_1, d_sample$ctc_prop_1)
cor.test(d_sample$ctc_hour_max_1, d_sample$ctc_prop_1)

cor.test(d_sample$awc_hour_max_1, d_sample$ctc_hour_max_1)
cor.test(d_sample$awc_prop_1, d_sample$ctc_prop_1)

cor.test(d_sample$awc_hour_max_1, d_sample$cvc_hour_max_1)
cor.test(d_sample$ctc_hour_max_1, d_sample$cvc_hour_max_1)

cor.test(d_sample$awc_prop_1, d_sample$cvc_hour_max_1)
cor.test(d_sample$ctc_prop_1, d_sample$cvc_hour_max_1)

# birth weight
cor.test(d_sample$awc_hour_max_1, d_sample$birth_weight_total_lbs)
cor.test(d_sample$awc_prop_1, d_sample$birth_weight_total_lbs)
cor.test(d_sample$ctc_hour_max_1, d_sample$birth_weight_total_lbs)
cor.test(d_sample$cvc_hour_max_1, d_sample$birth_weight_total_lbs)
cor.test(d_sample$ctc_prop_1, d_sample$birth_weight_total_lbs)
```

## Connectivity measures
```{r}
connect_corr <- 
  d_sample %>% 
  select(
    temp_coherence_z,
    front_coherence_z,
    age_scan_corr,
    gestational_weeks_birth,
    birth_weight_total_lbs,
    education,
    mom_age,
    income_needs,
    shipley_6mo_total,
    digitspan_totalscore,
    pregnancy_weight_diff,
    NEG,
    REG, 
    SUR
  ) %>% 
  correlate(method = "spearman") %>% 
  mutate_at(
    vars(-rowname),
    funs(round(., 3))
  )

write_csv(connect_corr, paste0(data_home_personal, "language/connect_covariates.csv"))

cor.test(d_sample$front_coherence_z, d_sample$education, method = "spearman")
cor.test(d_sample$temp_coherence_z, d_sample$shipley_6mo_total)
cor.test(d_sample$temp_coherence_z, d_sample$NEG)
```

## Frame-wise displacement 
```{r}
fd_corr <- 
  d_sample %>% 
  select(
    rawFD,
    censoredFD,
    temp_coherence_z,
    front_coherence_z,
    ctc_hour_max_1,
    awc_hour_max_1,
    cvc_hour_max_1,
    ctc_prop_1,
    awc_prop_1
  ) %>% 
  correlate(method = "pearson") %>% 
  mutate_at(
    vars(-rowname),
    funs(round(., 3))
  )

write_csv(fd_corr, paste0(data_home_personal, "language/FD_LENA_connectivity.csv"))

cor.test(d_sample$censoredFD, d_sample$awc_prop_1)
```

## Sex differences
```{r}
d_sample %>% 
  group_by(male) %>% 
  summarise_at(
    vars(ctc_prop_1, ctc_hour_max_1, awc_prop_1, awc_hour_max_1, cvc_hour_max_1),
    funs(mean, sd), na.rm = TRUE
  )

t.test(d_sample$ctc_prop_1 ~ d_sample$male)
t.test(d_sample$ctc_hour_max_1 ~ d_sample$male)
t.test(d_sample$awc_prop_1 ~ d_sample$male)
t.test(d_sample$awc_hour_max_1 ~ d_sample$male)
t.test(d_sample$cvc_hour_max_1 ~ d_sample$male)
```

```{r}
d_sample %>% 
  group_by(male) %>% 
  summarise_at(
    vars(front_coherence_z, temp_coherence_z),
    funs(mean, sd), na.rm = TRUE
  )

t.test(d$front_coherence_z ~ d$male)
t.test(d$temp_coherence_z ~ d$male)
```

## Scanner differences
```{r}
scan_diff_front <- lm(front_coherence_z ~ scanner_6mo, data = d_sample)
anova(scan_diff_front)

scan_diff_temp <- lm(temp_coherence_z ~ scanner_6mo, data = d_sample)
anova(scan_diff_temp)
      
d_sample %>% 
  group_by(scanner_6mo) %>% 
  summarise_at(
    vars(front_coherence_z, temp_coherence_z),
    funs(mean, sd)
  )

d_sample %>% 
  count(scanner_6mo)
```

## Bilingual status differences 
```{r}
t.test(d_sample$ctc_prop_1 ~ d_sample$primary_english)
t.test(d_sample$ctc_hour_max_1 ~ d_sample$primary_english)
t.test(d_sample$awc_prop_1 ~ d_sample$primary_english)
t.test(d_sample$awc_hour_max_1 ~ d_sample$primary_english)
t.test(d_sample$cvc_hour_max_1 ~ d_sample$primary_english)
```

```{r}
t.test(d$front_coherence_z ~ d$primary_english)
t.test(d$temp_coherence_z ~ d$primary_english)
```

# Models

## Contrast coding for binary and categorical variables
```{r}
d_sample <-
  d_sample %>% 
  mutate(scanner_6mo = as.factor(scanner_6mo))

contrasts(d_sample$scanner_6mo) <- cbind(
  CNIv3T2 = c(-1/3, 2/3, -1/3), 
  CNIv3T3 = c(2/3, -1/3, -1/3)
)
```

## Base models
```{r}
mlm_base1 <- lm(
  cbind(temp_coherence_z, front_coherence_z) ~ 
    scanner_6mo +
    education,
    data = d_sample
)
Anova(mlm_base1)

# dropping education: did not improve model fit

mlm_base2 <- lm(
  cbind(temp_coherence_z, front_coherence_z) ~ 
    scanner_6mo,
    data = d_sample
)
Anova(mlm_base2)

r.squaredT_base <- summary_base2$`Response temp_coherence_z`$r.squared
r.squaredF_base <- summary_base2$`Response front_coherence_z`$r.squared
```

## Quantity of language exposure

### AW
```{r}
mlm_AWq <- lm(
  cbind(scale(temp_coherence_z), scale(front_coherence_z)) ~ 
    scanner_6mo +
    scale(awc_hour_max_1),
    data = d_sample
)
Manova(mlm_AWq)
```

### CT
```{r}
mlm_CTq <- lm(
  cbind(scale(temp_coherence_z), scale(front_coherence_z)) ~ 
    scanner_6mo +
    scale(ctc_hour_max_1),
    data = d_sample
)
summary(mlm_CTq)
Manova(mlm_CTq)

lm_CTq_temp <- lm(
  scale(temp_coherence_z) ~
    scanner_6mo +
    scale(ctc_hour_max_1),
  data = d_sample
)
confint(lm_CTq_temp)

summary_CTq <- summary(mlm_CTq)
r.squaredT_CTq <- summary_CTq$`Response scale(temp_coherence_z)`$r.squared
r.sauaredT_delta_CTq <- r.squaredT_CTq - r.squaredT_base

model_d_ctcq <-
  d_sample %>% 
  select(
    temp_coherence_z,
    scanner_6mo,
    ctc_hour_max_1
  )

bayesianLR = generalTestBF(temp_coherence_z ~ ., data = model_d_ctcq)
```

## Consistency of language exposure 

### AW
```{r}
mlm_AWc <- lm(
  cbind(scale(temp_coherence_z), scale(front_coherence_z)) ~ 
    scanner_6mo +
    scale(awc_prop_1),
    data = d_sample
)
summary(mlm_AWc)
Anova(mlm_AWc)
```

### CT
```{r}
mlm_CTc <- lm(
  cbind(scale(temp_coherence_z), scale(front_coherence_z)) ~ 
    scanner_6mo +
    scale(ctc_prop_1),
    data = d_sample
)
summary(mlm_CTc)
Anova(mlm_CTc)
```

## Sensitivity analyses: Infant vocalizations
```{r}
mlm_CVq <- lm(
  cbind(scale(temp_coherence_z), scale(front_coherence_z)) ~ 
    scanner_6mo +
    scale(cvc_hour_max_1),
    data = d_sample
)
Manova(mlm_CVq)
summary(mlm_CVq)

lm_CVq_temp <- lm(
  scale(temp_coherence_z) ~
    scanner_6mo +
    scale(cvc_hour_max_1),
  data = d_sample
)
confint(lm_CVq_temp)

summary_CVq <- summary(mlm_CVq)
r.squaredT_CVq <- summary_CVq$`Response scale(temp_coherence_z)`$r.squared
r.sauaredT_delta_CVq <- r.squaredT_CVq - r.squaredT_base

model_d_cvcq <-
  d_sample %>% 
  select(
    temp_coherence_z,
    scanner_6mo,
    cvc_hour_max_1
  )

bayesianLR = generalTestBF(temp_coherence_z ~ ., data = model_d_cvcq)
```

## Sensitivity analyses: Connectivity values thresholded at .05 and .1

### Quantity of language exposure

#### AW
```{r}
mlm_AWq.1 <- lm(
  cbind(scale(temp_coherence_z.1), scale(front_coherence_z.1)) ~ 
    scanner_6mo +
    scale(awc_hour_max_1),
    data = d_sample
)
Manova(mlm_AWq.1)

mlm_AWq.05 <- lm(
  cbind(scale(temp_coherence_z.05), scale(front_coherence_z.05)) ~ 
    scanner_6mo +
    scale(awc_hour_max_1),
    data = d_sample
)
Manova(mlm_AWq.05)
```

#### CT
```{r}
mlm_CTq.1 <- lm(
  cbind(scale(temp_coherence_z.1), scale(front_coherence_z.1)) ~ 
    scanner_6mo +
    scale(ctc_hour_max_1),
    data = d_sample
)
Manova(mlm_CTq.1)

mlm_CTq.05 <- lm(
  cbind(scale(temp_coherence_z.05), scale(front_coherence_z.05)) ~ 
    scanner_6mo +
    scale(ctc_hour_max_1),
    data = d_sample
)
Manova(mlm_CTq.05)
```

### Consistency of language exposure

#### AW
```{r}
mlm_AWc.1 <- lm(
  cbind(scale(temp_coherence_z.1), scale(front_coherence_z.1)) ~ 
    scanner_6mo +
    scale(awc_prop_1),
    data = d_sample
)
Manova(mlm_AWc.1)

mlm_AWc.05 <- lm(
  cbind(scale(temp_coherence_z.05), scale(front_coherence_z.05)) ~ 
    scanner_6mo +
    scale(awc_prop_1),
    data = d_sample
)
Manova(mlm_AWc.05)
```

#### CT
```{r}
mlm_CTc.1 <- lm(
  cbind(scale(temp_coherence_z.1), scale(front_coherence_z.1)) ~ 
    scanner_6mo +
    scale(ctc_prop_1),
    data = d_sample
)
Manova(mlm_CTc.1)

mlm_CTc.05 <- lm(
  cbind(scale(temp_coherence_z.05), scale(front_coherence_z.05)) ~ 
    scanner_6mo +
    scale(ctc_prop_1),
    data = d_sample
)
Manova(mlm_CTc.05)
```


# Visualize effects

```{r}
d_sample %>% 
  ggplot(aes(ctc_hour_max_1, temp_coherence_z)) +
  geom_point(size = 3, alpha = 1/2) +
  geom_smooth(method = "lm", size = 2, color = "black") +
  scale_x_continuous(breaks = seq.int(25, 150, 25)) +
  scale_y_continuous(breaks = seq.int(-.2, .4, .1)) +
  theme_minimal() +
  theme(
    strip.text = element_text(size = 17),
    panel.grid = element_blank(),
    plot.title = element_text(size = 18, hjust = .5),
    axis.title = element_text(size = 18),
    axis.text = element_text(size = 16),
    legend.position = "none"
  ) +
  labs(
    x = "Quantity of conversational turns",
    y = "Posterior temporal\nnetwork connectivity (z)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/ctc_temp.png",
  width = 6,
  height = 4
)
```



