---
title: "Tidy infant rs-fMRI data"
author: "Lucy King"
date: "2/3/2020"
output: html_document
---

# Environment setup 
```{r}
library(tidyverse)
library(psych)
library(ggpubr)

results <- "~/Box/lucy_king_files/BABIES/rsfMRI/data/language/correlation_matrix/"
cc_file <- "~/Box/lucy_king_files/BABIES/rsfMRI/data/language/conn_cc_data.csv"
results_smoothed <- "~/Box/lucy_king_files/BABIES/rsfMRI/data/language/correlation_matrix_BOLDsmoothing/"
results_noGSR <- "~/Box/lucy_king_files/BABIES/rsfMRI/data/language/correlation_matrix_nogsr/"
demo_file <- "~/Box/Mooddata_Coordinating/BABIES/Data/final_scored_data/demographics/demo_6mo_cleaned_final.csv"
```

# no BOLD smoothing 

```{r warning=FALSE}
dirs_nosmoothing <- grep("[0-9]$", list.dirs(results, recursive = FALSE), value = TRUE)

files_nosmoothing <-
  tibble(
    path = 
      list.files(
        path = dirs_nosmoothing,
        pattern = "correlation_matrix.csv",
        full.names = TRUE,
        no.. = TRUE
      )
  ) 
```

## Read in individual-level data 
```{r warning=FALSE}
rs_matrix <- 
  files_nosmoothing %>% 
  mutate(
    data = map(
      path,
      read_csv
    )
  ) %>% 
  unnest(data) %>% 
  mutate(
    ID = as.numeric(str_extract(path, "\\d{4}"))
  ) %>% 
  dplyr::select(
    ID,
    everything(),
    -path
  ) 

```

```{r}
rs <- 
  rs_matrix %>% 
  gather(key, value, `left temporal pole`:`left_front_operc`) %>% 
  arrange(ID) %>% 
  rename(region_name = X1) %>% 
  mutate(
    region_name = dplyr::recode(
      region_name,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    ),
    key = dplyr::recode(
      key,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    )
  ) %>% 
  unite("key", region_name, key, sep = "_") %>% 
  filter(value != 1) %>% 
  spread(key, value) %>% 
  dplyr::select(
    ID,
    aud_foperc:aud_TP,
    foperc_IFGop:foperc_TP,
    IFGop_IFGor:IFGop_TP,
    IFGor_IFGtr:IFGor_TP,
    IFGtr_lTPJ:IFGtr_TP,
    lTPJ_rTPJ:lTPJ_TP,
    rTPJ_STS:rTPJ_TP,
    STS_TP
  ) %>% 
  # threshold correlations at .1 
  mutate_at(
    vars(-ID),
    funs(
      ".1" =
      if_else(abs(.) < .1, NA_real_, .)
    )
  )
 
```

## Read in clustering coefficient data and coherence data defined by iterative Louvain community detection; merge with other data

```{r}
rs_dd <-
  read_csv(cc_file) %>% 
  rename(ID = X1) %>% 
  mutate(ID = as.integer(ID)) %>% 
  rename(
    front_dd_p = N1_corr,
    temp_dd_p = N2_corr,
    front_cc = N1_cc,
    temp_cc = N2_cc
  ) 

rs <-
  rs %>% 
  left_join(rs_dd, by = "ID")
```

# 4mm BOLD signal smoothing kernal
```{r warning=FALSE}
dirs_4mm <- grep("[0-9]", list.dirs(results_smoothed, recursive = FALSE), value = TRUE)

files_4mm <-
  tibble(
    path = 
      list.files(
        path = paste0(dirs_4mm, "/_fwhm_4/"),
        pattern = "correlation_matrix.csv",
        full.names = TRUE,
        no.. = TRUE
      )
  ) 

```

## Read in individual-level data 
```{r, warning=FALSE}
rs_4mm_matrix <- 
  files_4mm %>% 
  mutate(
    data = map(
      path,
      read_csv
    )
  ) %>% 
  unnest(data) %>% 
  mutate(
    ID = as.numeric(str_extract(path, "\\d{4}"))
  ) %>% 
  dplyr::select(
    ID,
    everything(),
    -path
  ) 
```

```{r}
rs_4mm <- 
  rs_4mm_matrix %>% 
  gather(key, value, `left temporal pole`:`left_front_operc`) %>% 
  arrange(ID) %>% 
  rename(region_name = X1) %>% 
  mutate(
    region_name = dplyr::recode(
      region_name,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    ),
    key = dplyr::recode(
      key,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    )
  ) %>% 
  unite("key", region_name, key, sep = "_") %>% 
  filter(value != 1) %>% 
  spread(key, value) %>% 
  dplyr::select(
    ID,
    aud_foperc:aud_TP,
    foperc_IFGop:foperc_TP,
    IFGop_IFGor:IFGop_TP,
    IFGor_IFGtr:IFGor_TP,
    IFGtr_lTPJ:IFGtr_TP,
    lTPJ_rTPJ:lTPJ_TP,
    rTPJ_STS:rTPJ_TP,
    STS_TP
  ) %>% 
  rename_at(
    vars(-ID),
    funs(
      . %>% 
      paste0("_4mm")
    )
  )
```

# 8mm BOLD signal smoothing kernal
```{r warning=FALSE}
dirs_8mm <- grep("[0-9]", list.dirs(results_smoothed, recursive = FALSE), value = TRUE)

files_8mm <-
  tibble(
    path = 
      list.files(
        path = paste0(dirs_4mm, "/_fwhm_8/"),
        pattern = "correlation_matrix.csv",
        full.names = TRUE,
        no.. = TRUE
      )
  ) 

```

## Read in individual-level data 
```{r, warning = FALSE}
rs_8mm_matrix <- 
  files_8mm %>% 
  mutate(
    data = map(
      path,
      read_csv
    )
  ) %>% 
  unnest(data) %>% 
  mutate(
    ID = as.numeric(str_extract(path, "\\d{4}"))
  ) %>% 
  dplyr::select(
    ID,
    everything(),
    -path
  ) 
```

```{r}
rs_8mm <- 
  rs_8mm_matrix %>% 
  gather(key, value, `left temporal pole`:`left_front_operc`) %>% 
  arrange(ID) %>% 
  rename(region_name = X1) %>% 
  mutate(
    region_name = dplyr::recode(
      region_name,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    ),
    key = dplyr::recode(
      key,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    )
  ) %>% 
  unite("key", region_name, key, sep = "_") %>% 
  filter(value != 1) %>% 
  spread(key, value) %>% 
  dplyr::select(
    ID,
    aud_foperc:aud_TP,
    foperc_IFGop:foperc_TP,
    IFGop_IFGor:IFGop_TP,
    IFGor_IFGtr:IFGor_TP,
    IFGtr_lTPJ:IFGtr_TP,
    lTPJ_rTPJ:lTPJ_TP,
    rTPJ_STS:rTPJ_TP,
    STS_TP
  ) %>% 
  rename_at(
    vars(-ID),
    funs(
      . %>% 
      paste0("_8mm")
    )
  )
```

# No GSR
```{r warning = FALSE}
dirs_nGSR <- grep("[0-9]$", list.dirs(results_noGSR, recursive = FALSE), value = TRUE)

files_noGSR <-
  tibble(
    path = 
      list.files(
        path = dirs_nGSR,
        pattern = "correlation_matrix.csv",
        full.names = TRUE,
        no.. = TRUE
      )
  ) 
```

## Read in individual-level data 
```{r, warning = FALSE}
rs_noGSR_matrix <- 
  files_noGSR %>% 
  mutate(
    data = map(
      path,
      read_csv
    )
  ) %>% 
  unnest(data) %>% 
  mutate(
    ID = as.numeric(str_extract(path, "\\d{4}"))
  ) %>% 
  dplyr::select(
    ID,
    everything(),
    -path
  ) 
```

```{r}
rs_noGSR <- 
  rs_noGSR_matrix %>% 
  gather(key, value, `left temporal pole`:`left_front_operc`) %>% 
  arrange(ID) %>% 
  rename(region_name = X1) %>% 
  mutate(
    region_name = dplyr::recode(
      region_name,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    ),
    key = dplyr::recode(
      key,
      "left temporal pole" = "TP",
      "left STS" = "STS",
      "right TPJ" = "rTPJ",
      "left TPJ" = "lTPJ",
      "left IFG (opercularis)" = "IFGop",
      "left IFG (triangularis)" = "IFGtr",
      "left IFG (orbitalis)" = "IFGor",
      "left_aud_cortex" = "aud",
      "left_front_operc" = "foperc"
    )
  ) %>% 
  unite("key", region_name, key, sep = "_") %>% 
  filter(value != 1) %>% 
  spread(key, value) %>% 
  dplyr::select(
    ID,
    aud_foperc:aud_TP,
    foperc_IFGop:foperc_TP,
    IFGop_IFGor:IFGop_TP,
    IFGor_IFGtr:IFGor_TP,
    IFGtr_lTPJ:IFGtr_TP,
    lTPJ_rTPJ:lTPJ_TP,
    rTPJ_STS:rTPJ_TP,
    STS_TP
  ) %>% 
  rename_at(
    vars(-ID),
    funs(
      . %>% 
      paste0("_noGSR")
    )
  )

```

# Merge all files
```{r, warning=FALSE}
rs <-
  rs %>% 
  left_join(rs_4mm, by = "ID") %>% 
  left_join(rs_8mm, by = "ID") %>% 
  left_join(rs_noGSR, by = "ID") %>% 
  left_join(read_csv(demo_file), by = "ID")
```

# Compute coherence for networks defined by visual inspection of adjacency matrix

Overall network:
left temporal pole
left STS
right TPJ
left TPJ
left IFG (opercularis)
left IFG (triangularis)
left IFG (orbitalis)
left_aud_cortex
left_front_operc

Subnetwork 1 (frontal/top-down):
left temporal pole
left IFG (opercularis)
left IFG (triangularis)
left IFG (orbitalis)
left_front_operc

Subnetwork 2 (temporal/bottom-up):
left STS
right TPJ
left TPJ
left_aud_cortex

## no spatial smoothing data 
```{r}
# no threshold__________________________________________________________________
all_rois <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor,
    IFGop_IFGtr,
    IFGor_IFGtr,
    IFGop_TP,
    IFGor_TP,
    IFGtr_TP,
    foperc_IFGop,
    foperc_IFGor,
    foperc_IFGtr,
    foperc_TP,
    rTPJ_STS,
    lTPJ_STS,
    lTPJ_rTPJ,
    aud_lTPJ,
    aud_rTPJ,
    aud_STS
  ) %>% 
  names()

front_rois <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor,
    IFGop_IFGtr,
    IFGor_IFGtr,
    IFGop_TP,
    IFGor_TP,
    IFGtr_TP,
    foperc_IFGop,
    foperc_IFGor,
    foperc_IFGtr,
    foperc_TP
  ) %>% 
  names()

temp_rois <-
  rs %>% 
  dplyr::select(
    rTPJ_STS,
    lTPJ_STS,
    lTPJ_rTPJ,
    aud_lTPJ,
    aud_rTPJ,
    aud_STS
  ) %>% 
  names()
```

```{r}
# .1 threshold__________________________________________________________________
all_rois.1 <-
  rs %>% 
  dplyr::select(contains(".1")) %>% 
  names()

front_rois.1 <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_.1,
    IFGop_IFGtr_.1,
    IFGor_IFGtr_.1,
    IFGop_TP_.1,
    IFGor_TP_.1,
    IFGtr_TP_.1,
    foperc_IFGop_.1,
    foperc_IFGor_.1,
    foperc_IFGtr_.1,
    foperc_TP_.1
  ) %>% 
  names()

temp_rois.1 <-
  rs %>% 
  dplyr::select(
    rTPJ_STS_.1,
    lTPJ_STS_.1,
    lTPJ_rTPJ_.1,
    aud_lTPJ_.1,
    aud_rTPJ_.1,
    aud_STS_.1
  ) %>% 
  names()

```

```{r}
rs <- 
  rs %>% 
  mutate(
    # no threshold
    av_coherence_p = 
      pmap_dbl(
        dplyr::select(., all_rois),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    av_coherence_z = fisherz(av_coherence_p),
    front_coherence_p = 
      pmap_dbl(
        dplyr::select(., front_rois),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    front_coherence_z = fisherz(front_coherence_p),
    temp_coherence_p = 
      pmap_dbl(
        dplyr::select(., temp_rois),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    temp_coherence_z = fisherz(temp_coherence_p),
    front_coherence_p.1 = 
      pmap_dbl(
        dplyr::select(., front_rois.1),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    front_coherence_z.1 = fisherz(front_coherence_p.1),
    temp_coherence_p.1 = 
      pmap_dbl(
        dplyr::select(., temp_rois.1),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    temp_coherence_z.1 = fisherz(temp_coherence_p.1)
  )
```

## 4mm data 
```{r}
# no threshold__________________________________________________________________
all_rois_4mm <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_4mm,
    IFGop_IFGtr_4mm,
    IFGor_IFGtr_4mm,
    IFGop_TP_4mm,
    IFGor_TP_4mm,
    IFGtr_TP_4mm,
    foperc_IFGop_4mm,
    foperc_IFGor_4mm,
    foperc_IFGtr_4mm,
    foperc_TP_4mm,
    rTPJ_STS_4mm,
    lTPJ_STS_4mm,
    lTPJ_rTPJ_4mm,
    aud_lTPJ_4mm,
    aud_rTPJ_4mm,
    aud_STS_4mm
  ) %>% 
  names()

front_rois_4mm <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_4mm,
    IFGop_IFGtr_4mm,
    IFGor_IFGtr_4mm,
    IFGop_TP_4mm,
    IFGor_TP_4mm,
    IFGtr_TP_4mm,
    foperc_IFGop_4mm,
    foperc_IFGor_4mm,
    foperc_IFGtr_4mm,
    foperc_TP_4mm
  ) %>% 
  names()

temp_rois_4mm <-
  rs %>% 
  dplyr::select(
    rTPJ_STS_4mm,
    lTPJ_STS_4mm,
    lTPJ_rTPJ_4mm,
    aud_lTPJ_4mm,
    aud_rTPJ_4mm,
    aud_STS_4mm
  ) %>% 
  names()

```

```{r}
rs <- 
  rs %>% 
  mutate(
    # no threshold
    av_coherence_p_4mm = 
      pmap_dbl(
        dplyr::select(., all_rois_4mm),
        function(...) mean(c(...), na.rm = TRUE)
    ),
    av_coherence_z_4mm = fisherz(av_coherence_p_4mm),
    front_coherence_p_4mm = 
      pmap_dbl(
        dplyr::select(., front_rois_4mm),
        function(...) mean(c(...), na.rm = TRUE)
    ),
    front_coherence_z_4mm = fisherz(front_coherence_p_4mm),
    temp_coherence_p_4mm = 
      pmap_dbl(
        dplyr::select(., temp_rois_4mm),
        function(...) mean(c(...), na.rm = TRUE)
    ),
    temp_coherence_z_4mm = fisherz(temp_coherence_p_4mm)
  )
```

## 8mm data 
```{r}
# no threshold__________________________________________________________________
all_rois_8mm <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_8mm,
    IFGop_IFGtr_8mm,
    IFGor_IFGtr_8mm,
    IFGop_TP_8mm,
    IFGor_TP_8mm,
    IFGtr_TP_8mm,
    foperc_IFGop_8mm,
    foperc_IFGor_8mm,
    foperc_IFGtr_8mm,
    foperc_TP_8mm,
    rTPJ_STS_8mm,
    lTPJ_STS_8mm,
    lTPJ_rTPJ_8mm,
    aud_lTPJ_8mm,
    aud_rTPJ_8mm,
    aud_STS_8mm
  ) %>% 
  names()

front_rois_8mm <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_8mm,
    IFGop_IFGtr_8mm,
    IFGor_IFGtr_8mm,
    IFGop_TP_8mm,
    IFGor_TP_8mm,
    IFGtr_TP_8mm,
    foperc_IFGop_8mm,
    foperc_IFGor_8mm,
    foperc_IFGtr_8mm,
    foperc_TP_8mm
  ) %>% 
  names()

temp_rois_8mm <-
  rs %>% 
  dplyr::select(
    rTPJ_STS_8mm,
    lTPJ_STS_8mm,
    lTPJ_rTPJ_8mm,
    aud_lTPJ_8mm,
    aud_rTPJ_8mm,
    aud_STS_8mm
  ) %>% 
  names()

```

```{r}
rs <- 
  rs %>% 
  mutate(
    # no threshold
    av_coherence_p_8mm = 
      pmap_dbl(
        dplyr::select(., all_rois_8mm),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    av_coherence_z_8mm = fisherz(av_coherence_p_8mm),
    front_coherence_p_8mm = 
      pmap_dbl(
        dplyr::select(., front_rois_8mm),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    front_coherence_z_8mm = fisherz(front_coherence_p_8mm),
    temp_coherence_p_8mm = 
      pmap_dbl(
        dplyr::select(., temp_rois_8mm),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    temp_coherence_z_8mm = fisherz(temp_coherence_p_8mm)
  )
```

## no GSR
```{r}
# no threshold__________________________________________________________________
all_rois_noGSR <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_noGSR,
    IFGop_IFGtr_noGSR,
    IFGor_IFGtr_noGSR,
    IFGop_TP_noGSR,
    IFGor_TP_noGSR,
    IFGtr_TP_noGSR,
    foperc_IFGop_noGSR,
    foperc_IFGor_noGSR,
    foperc_IFGtr_noGSR,
    foperc_TP_noGSR,
    rTPJ_STS_noGSR,
    lTPJ_STS_noGSR,
    lTPJ_rTPJ_noGSR,
    aud_lTPJ_noGSR,
    aud_rTPJ_noGSR,
    aud_STS_noGSR
  ) %>% 
  names()

front_rois_noGSR <-
  rs %>% 
  dplyr::select(
    IFGop_IFGor_noGSR,
    IFGop_IFGtr_noGSR,
    IFGor_IFGtr_noGSR,
    IFGop_TP_noGSR,
    IFGor_TP_noGSR,
    IFGtr_TP_noGSR,
    foperc_IFGop_noGSR,
    foperc_IFGor_noGSR,
    foperc_IFGtr_noGSR,
    foperc_TP_noGSR
  ) %>% 
  names()

temp_rois_noGSR <-
  rs %>% 
  dplyr::select(
    rTPJ_STS_noGSR,
    lTPJ_STS_noGSR,
    lTPJ_rTPJ_noGSR,
    aud_lTPJ_noGSR,
    aud_rTPJ_noGSR,
    aud_STS_noGSR
  ) %>% 
  names()
```

```{r}
rs <- 
  rs %>% 
  mutate(
    # no threshold
    av_coherence_p_noGSR = 
      pmap_dbl(
        dplyr::select(., all_rois_noGSR),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    av_coherence_z_noGSR = fisherz(av_coherence_p_noGSR),
    front_coherence_p_noGSR = 
      pmap_dbl(
        dplyr::select(., front_rois_noGSR),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    front_coherence_z_noGSR = fisherz(front_coherence_p_noGSR),
    temp_coherence_p_noGSR = 
      pmap_dbl(
        dplyr::select(., temp_rois_noGSR),
        function(...) mean(c(...), na.rm = TRUE)
      ),
    temp_coherence_z_noGSR = fisherz(temp_coherence_p_noGSR)
  )
```

## Fisher z transform for coherence of networks defined by Louvain community detection
```{r}
rs <-
  rs %>% 
  mutate(
    front_dd_z = fisherz(front_dd_p),
    temp_dd_z = fisherz(temp_dd_p)
  )
```

# Histograms

## no spatial smoothing coherence data defined by visual inspection
```{r}
hist_front_ns <-
  rs %>% 
  ggplot(aes(front_coherence_z)) +
  geom_histogram(binwidth = .05) +
  geom_vline(
    xintercept = mean(rs$front_coherence_z) + 3*sd(rs$front_coherence_z),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$front_coherence_z) - 3*sd(rs$front_coherence_z),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  theme_pubr() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the frontotemporal network (z)"
  )

hist_front_ns

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/fronto_hist.png",
  width = 5,
  height = 4
)

hist_post_ns <-
  rs %>% 
  ggplot(aes(temp_coherence_z)) +
  geom_histogram(binwidth = .05) +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z) + 3*sd(rs$temp_coherence_z),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z) - 3*sd(rs$temp_coherence_z),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the posterior temporal network (z)\n(no spatial smoothing)"
  )

hist_post_ns

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/posterior_hist.png",
  width = 5,
  height = 4
)

hists_nosmoothing <-
  ggarrange(
  hist_front_ns + rremove("x.title"),
  hist_post_ns + rremove("x.title") + rremove("y.title"),
  labels = c(
    "A",
    "B"
  ),
  align = "v"
)

hists_nosmoothing <- 
  annotate_figure(
  hists_nosmoothing,
  bottom = text_grob("Connectivity (z) in frontotemporal (A) and posterior temporal (B) networks ", size = 16)
)

hists_nosmoothing

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/hists_ns.png",
  width = 10,
  height = 4
)
```

## no spatial smoothing coherence data defined by Louvain community detection
```{r}
hist_front_dd <-
  rs %>% 
  ggplot(aes(front_dd_z)) +
  geom_histogram(binwidth = .05) +
  geom_vline(
    xintercept = mean(rs$front_dd_z) + 3*sd(rs$front_dd_z),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$front_dd_z) - 3*sd(rs$front_dd_z),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the frontotemporal network (z)\ndefined by Louvain community detection"
  )

hist_front_dd

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/fronto_dd_hist.png",
  width = 5,
  height = 4
)

hist_post_dd <-
  rs %>% 
  ggplot(aes(temp_dd_z)) +
  geom_histogram(binwidth = .05) +
  geom_vline(
    xintercept = mean(rs$temp_dd_z) + 3*sd(rs$temp_dd_z),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$temp_dd_z) - 3*sd(rs$temp_dd_z),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the posterior temporal network (z)\ndefined by Louvain community detection"
  )

hist_post_dd

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/posterior_dd_hist.png",
  width = 5,
  height = 4
)

hists_dd <-
  ggarrange(
  hist_front_dd + rremove("x.title"),
  hist_post_dd + rremove("x.title") + rremove("y.title"),
  labels = c(
    "A",
    "B"
  ),
  align = "v"
)

hists_dd <- 
  annotate_figure(
  hists_dd,
  bottom = text_grob("Connectivity (z) in frontotemporal (A) and posterior temporal (B) networks\ndefined by Louvain community detection", size = 16)
)

hists_dd

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/hists_dd.png",
  width = 10,
  height = 4
)
```

## 4mm smoothing coherence data 
```{r}
hist_front_4mm <-
  rs %>% 
  ggplot(aes(front_coherence_z_4mm)) +
  geom_histogram() +
  geom_vline(
    xintercept = mean(rs$front_coherence_z_4mm) + 3*sd(rs$front_coherence_z_4mm),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$front_coherence_z_4mm) - 3*sd(rs$front_coherence_z_4mm),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  labs(
    x = "Connectivity in the frontotemporal network (z)\n(4mm smoothing kernal)"
  )

hist_front_4mm

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/fronto_4mm_hist.png",
  width = 5,
  height = 4
)

hist_post_4mm <- 
  rs %>% 
  ggplot(aes(temp_coherence_z_4mm)) +
  geom_histogram() +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z_4mm) + 3*sd(rs$temp_coherence_z_4mm),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z_4mm) - 3*sd(rs$temp_coherence_z_4mm),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  labs(
    x = "Connectivity in the posterior temporal network (z)\n(4mm smoothing kernal)"
  )

hist_post_4mm

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/posterior_4mm_hist.png",
  width = 5,
  height = 4
)
```

## 8mm smoothing coherence data 
```{r}
rs %>% 
  ggplot(aes(front_coherence_z_8mm)) +
  geom_histogram() +
  geom_vline(
    xintercept = mean(rs$front_coherence_z_8mm) + 3*sd(rs$front_coherence_z_8mm),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$front_coherence_z_8mm) - 3*sd(rs$front_coherence_z_8mm),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  labs(
    x = "Connectivity in the frontotemporal network (z)\n(8mm smoothing kernal)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/fronto_8mm_hist.png",
  width = 5,
  height = 4
)

rs %>% 
  ggplot(aes(temp_coherence_z_8mm)) +
  geom_histogram() +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z_8mm) + 3*sd(rs$temp_coherence_z_8mm),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z_8mm) - 3*sd(rs$temp_coherence_z_8mm),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  labs(
    x = "Connectivity in the posterior temporal network (z)\n(8mm smoothing kernal)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/posterior_8mm_hist.png",
  width = 5,
  height = 4
)
```

## no GSR coherence data 
```{r}
hist_front_noGSR <- 
  rs %>% 
  ggplot(aes(front_coherence_z_noGSR)) +
  geom_histogram(binwidth = .05) +
  geom_vline(
    xintercept = mean(rs$front_coherence_z_noGSR) + 3*sd(rs$front_coherence_z_noGSR),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$front_coherence_z_noGSR) - 3*sd(rs$front_coherence_z_noGSR),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(0, 1, .2)) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the frontotemporal network (z)\n(no spatial smoothing, no GSR)"
  )

hist_front_noGSR

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/fronto_noGSR_hist.png",
  width = 5,
  height = 4
)

hist_post_noGSR <- 
  rs %>% 
  ggplot(aes(temp_coherence_z_noGSR)) +
  geom_histogram(binwidth = .05) +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z_noGSR) + 3*sd(rs$temp_coherence_z_noGSR),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$temp_coherence_z_noGSR) - 3*sd(rs$temp_coherence_z_noGSR),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(0, 1, .2)) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the posterior temporal network (z)\n(no spatial smoothing, no GSR)"
  )

hist_post_noGSR

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/posterior_noGSR_hist.png",
  width = 5,
  height = 4
)

hists_noGSR <-
  ggarrange(
  hist_front_noGSR + rremove("x.title"),
  hist_post_noGSR + rremove("x.title") + rremove("y.title"),
  labels = c(
    "A",
    "B"
  ),
  align = "v"
)

hists_noGSR <- 
  annotate_figure(
  hists_noGSR,
  bottom = text_grob("Connectivity (z) in frontotemporal (A) and posterior temporal (B) networks\nwithout mean signal regression", size = 16)
)

hists_noGSR

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/hists_noGSR.png",
  width = 10,
  height = 4
)
```

## Clustering coefficients
```{r}
rs %>%
  ggplot(aes(front_cc)) +
  geom_histogram() +
  geom_vline(
    xintercept = mean(rs$front_cc) + 3*sd(rs$front_cc),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$front_cc) - 3*sd(rs$front_cc),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  labs(
    x = "Clustering coefficient of the frontotemporal network (z)\n(no spatial smoothing)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/front_cc_hist.png",
  width = 5,
  height = 4
)

rs %>%
  ggplot(aes(temp_cc)) +
  geom_histogram() +
  geom_vline(
    xintercept = mean(rs$temp_cc) + 3*sd(rs$temp_cc),
    color = "red"
  ) +
  geom_vline(
    xintercept = mean(rs$temp_cc) - 3*sd(rs$temp_cc),
    color = "red"
  ) +
  scale_x_continuous(breaks = seq.int(-.2, .8, .1)) +
  labs(
    x = "Clustering coefficient of the posterior temporal network (z)\n(no spatial smoothing)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/temp_cc_hist.png",
  width = 5,
  height = 4
)
```

```{r}
# remove outlier
rs %>% 
  filter(front_coherence_z > .6)

rs <-
  rs %>% 
  mutate(
    front_coherence_z = if_else(
      ID == 115, NA_real_,  front_coherence_z
    ),
    front_coherence_z_4mm = if_else(
      ID == 115, NA_real_,  front_coherence_z_4mm
    ),
    front_coherence_z_8mm = if_else(
      ID == 115, NA_real_,  front_coherence_z_8mm
    ),
    front_dd_z = if_else(
      ID == 115, NA_real_,  front_dd_z
    )
  )
```

# Associations between coherence and clustering coefficient measures

## Frontotemporal and posterior temporal coherence 

### Based on visual inspection
```{r}
rs %>% 
  ggplot(aes(temp_coherence_z, front_coherence_z)) +
  geom_point() +
  geom_smooth(method = "lm")

rs %>% 
  ggplot(aes(temp_coherence_z_4mm, front_coherence_z_4mm)) +
  geom_point() +
  geom_smooth(method = "lm")
```

### Based on Louvain community detection
```{r}
rs %>% 
  ggplot(aes(temp_dd_z, front_dd_z)) +
  geom_point() +
  geom_smooth(method = "lm")
```

## Coherence between no spatial smoothing and 4mm 
```{r}
rs %>% 
  ggplot(aes(front_coherence_z, front_coherence_z_4mm)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    x = "Connectivity in the frontotemporal network\n(no spatial smoothing)",
    y = "Connectivity in the frontotemporal network\n(4mm smoothing kernal)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/frontNOsmooth_front_4mm.png",
  width = 5,
  height = 4
)

cor.test(rs$front_coherence_z, rs$front_coherence_z_4mm)

rs %>% 
  ggplot(aes(temp_coherence_z, temp_coherence_z_4mm)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    x = "Connectivity in the posterior temporal network\n(no spatial smoothing)",
    y = "Connectivity in the posterior temporal network\n(4mm smoothing kernal)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/postNOsmooth_post_4mm.png",
  width = 5,
  height = 4
)

cor.test(rs$temp_coherence_z, rs$temp_coherence_z_4mm)
```

## Coherence between no spatial smoothing and 8mm 
```{r}
rs %>% 
  ggplot(aes(front_coherence_z, front_coherence_z_8mm)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    x = "Connectivity in the frontotemporal network\n(no spatial smoothing)",
    y = "Connectivity in the frontotemporal network\n(8mm smoothing kernal)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/frontNOsmooth_front_8mm.png",
  width = 5,
  height = 4
)

cor.test(rs$front_coherence_z, rs$front_coherence_z_8mm)

rs %>% 
  ggplot(aes(temp_coherence_z, temp_coherence_z_4mm)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    x = "Connectivity in the posterior temporal network\n(no spatial smoothing)",
    y = "Connectivity in the posterior temporal network\n(8mm smoothing kernal)"
  )

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/postNOsmooth_post_8mm.png",
  width = 5,
  height = 4
)

cor.test(rs$temp_coherence_z, rs$temp_coherence_z_8mm)
```

## Clustering coefficient and age 
```{r}
# GSR
age_front_cc <-
  rs %>% 
  ggplot(aes(age_scan_corr, front_cc)) +
  geom_point() +
  geom_smooth(method = "lm", span = 1) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Infant corrected age at scan (months)",
    y = "Local clustering coefficient"
  ) 

age_front_cc

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/age_frontcc.png",
  width = 5,
  height = 4
)

age_temp_cc <-
  rs %>% 
  ggplot(aes(age_scan_corr, temp_cc)) +
  geom_point() +
  geom_smooth(method = "lm", span = 1) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Infant corrected age at scan (months)",
    y = "Local clustering coefficient"
  )

age_temp_cc

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/age_tempcc.png",
  width = 5,
  height = 4
)


#all near 0 values treated as 0; and everything with a positive/negative magnitude treated as 1
```

## Clustering coefficient and coherence 
```{r}
# GSR
front_z_cc <-
  rs %>% 
  ggplot(aes(front_coherence_z, front_cc)) +
  geom_point() +
  geom_smooth(method = "loess", span = 1) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the frontotemporal network\n(with mean signal regression)",
    y = "Local clustering coefficient"
  ) 

front_z_cc

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/frontconn_frontcc.png",
  width = 5,
  height = 4
)

temp_z_cc <-
  rs %>% 
  ggplot(aes(temp_coherence_z, temp_cc)) +
  geom_point() +
  geom_smooth(method = "loess", span = 1) +
  theme_minimal() +
  theme(
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14)
  ) +
  labs(
    x = "Connectivity in the posterior temporal network\n(with mean signal regression)",
    y = "Local clustering coefficient"
  )

temp_z_cc

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/tempconn_tempcc.png",
  width = 5,
  height = 4
)


conn_cc <-
  ggarrange(
  front_z_cc + rremove("x.title"),
  temp_z_cc + rremove("x.title") + rremove("y.title"),
  labels = c(
    "A",
    "B"
  ),
  align = "v"
)

conn_cc <- 
  annotate_figure(
  conn_cc,
  bottom = text_grob("Connectivity (z) in frontotemporal (A) and posterior temporal (B) networks ", size = 16)
)

conn_cc

ggsave(
  "~/Box/lucy_king_files/BABIES/rsfMRI/LENA/figures/conn_cc.png",
  width = 10,
  height = 4
)

#all near 0 values treated as 0; and everything with a positive/negative magnitude treated as 1
```


```{r}
rs <-
  rs %>% 
  dplyr::select(-male:-income_needs)

#write_csv(rs, "~/Box/lucy_king_files/BABIES/rsfMRI/data/language/rs_tidy_20200821.csv")
```

